---
title: "Effectiveness of a Drug"
author: "Hannes Schiller"
date: "3/23/2020"
output: pdf_document
---
Load the Dataset
```{r}
test= read.csv("drugsCom_raw/drugsComTest_raw_csv.csv")
train= read.csv("drugsCom_raw/drugsComTrain_raw_csv.csv")
```
```{r}
train
```

Combine both datasets
```{r}
total <- rbind(test, train)
str(total)
```

Clean symbols
```{r}
total$review=gsub("&#039;","'", total$review)
str(total)
```

```{r}
library(tm)
corpus = Corpus(VectorSource(total$review))
corpus
```

Lower case
```{r}
corpus = tm_map(corpus, tolower)
```

Remove Punctuation 
```{r}
corpus = tm_map(corpus, removePunctuation)
```

Remove Stop words
```{r}
corpus = tm_map(corpus, removeWords, stopwords("english"))
```

Stem Words
```{r}
corpus = tm_map(corpus, stemDocument)
```

Bag of words matrix
```{r}
gc()
dtm = DocumentTermMatrix(corpus)
#dtm_mat=as.matrix(dtm)
dtm
```

Remove Sparse Terms at 95% accounted for
```{r}
spdtm = removeSparseTerms(dtm, 0.95)
spdtm
```

Convert to a data frame
```{r}
drugSparse = as.data.frame(as.matrix(spdtm))
drugSparse
```

Add dependent variable
```{r}
drugSparse$rating = total$rating

```

Split 80 20 split
```{r}
library(caTools)
set.seed(123)
split = sample.split(drugSparse$rating, SplitRatio = 0.8)
train = subset(drugSparse, split==TRUE)
test = subset(drugSparse, split==FALSE)
```

KKNN Mehod K=3
```{r}
library(kknn)
#k=3 this is the one that gave me 73% accuracy
system.time(model1 <- train.kknn(rating~.,data=train, ks=3))
#optimizer but I havent gotten it to run
#system.time(model2 <- train.kknn(rating~.,data=train))
model1
pred1=predict(model1, newdata=test)


pred1 = round(pred1,0)
test$output= ifelse(test$rating<= 3, "Adverse", ifelse(test$rating>=7, "Effective", "Ineffective"))

#create a datframe for predictions
pred1= data.frame(pred1)
#create column output
pred1$output= ifelse(pred1$pred1<= 3, "Adverse", ifelse(pred1$pred1>=7, "Effective", "Ineffective"))
#accuracy
acc1=mean(pred1$output==test$output)
acc1
```
72% Accuracy 

KKNN 
Allow the model to chose optimal K
```{r}
test$output=NULL
library(kknn)
system.time(model2 <- train.kknn(rating~.,data=train))
pred2=predict(model2, newdata=test)
test$output= ifelse(test$rating<= 3, "Adverse", ifelse(test$rating>=7, "Effective", "Ineffective"))
pred2= data.frame(pred2)
#create column output
pred2$output= ifelse(pred2$pred2<= 3, "Adverse", ifelse(pred2$pred2>=7, "Effective", "Ineffective"))
#accuracy
acc2=mean(pred2$output==test$output)
acc2

```
79% Accuracy


Ordinal Logistic Regression
```{r}
train$category= ifelse(train$output == "Adverse", 1, ifelse(train$output == "Effective", 3, 2))
test$category= ifelse(test$output == "Adverse", 1, ifelse(test$output == "Effective", 3, 2))
```
```{r}
# fit in logistic regression model
library(MASS)
logit <- polr(factor(category) ~ .-output - category -rating, data=train)
```
```{r}
preds <- predict(logit) #use model to do the prediction, more straight
mean(preds == train$category)
#the accuracy of prediction is about 70.15%
```
test dataset
```{r}
pred_logit = predict(logit, test)
```
```{r}
mean(pred_logit == test$category)
```
69.95% accuracy

```{r}
drugSparse=emailsSparse
drugSparse$drugname = total$drugName
drugSparse$output= ifelse(drugSparse$rating<= 3, "Adverse", ifelse(drugSparse$rating>=7, "Effective", "Ineffective"))
train$output= ifelse(train$rating<= 3, "Adverse", ifelse(train$rating>=7, "Effective", "Ineffective"))
test$output= ifelse(test$rating<= 3, "Adverse", ifelse(test$rating>=7, "Effective", "Ineffective"))
```



Confusion Matrix
```{r}
table(test$output, pred2$output)
```

